A holomorphic approach to membranes and fivebranes

### 2022-06-06 fivebranes/index.tex
all around

\section{The representation theory of local operators}

@@

\begin{dfn} 
Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
\end{dfn}

@@

In this paper we are interested in theories obtained from twists of supersymmetric theories. 
Generally speaking, such twists have a mixed holomorphic and topological behavior.
%Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
%Let $\cV$ denote its sheaf of holomorphic sections.
%The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
%\[
%\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
%\]
%where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
%Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
%
%As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
%\begin{itemize}
%\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
%\[
%[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
%\]
%\end{itemize}
%A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
%
%\parsec

Without loss of generality we will assume our holomorphic-topological local $L_\infty$ algebra on $M \times X$ is of the form
\beqn\label{eqn:cL}
\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
\eeqn
where $L$ is a graded holomorphic vector bundle on $X$.
The structure maps of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators. 
For more details we refer to the definitions in \cite{GRWthf}.

In part, the data of a holomorphic-topological theory in the BV formalism is prescribed by a holomorphic-topological local $L_\infty$ algebra. 
The factorization algebra of classical observables supported on an open set $U \subset M \times X$ is given by the Chevalley--Eilenberg cochain on the $L_\infty$ algebra $\cL(U)$. 
We will give a concise presentation for the {\em local} operators in a topological-holomorphic theory.

Suppose that $M \times X = \R^m \times \C^n$ and suppose that the bundle $L \to \C^n$ is translation invariant with fiber $L_0$ over $0 \in \R^m \times \C^n$.
We also assume that all structure maps of the $L_\infty$ algebra are translation invariant.
The jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras
\[
\cL(\C^n \times \R^m) \to L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] 
\]
The differential, or one-ary, operation of the $L_\infty$ algebra on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables. 
Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
\[
L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] \xto{\simeq} L_0 [[z_j]] 
\]
is a quasi-isomorphism. 
The only remaining differential on the right hand side is~$Q^{hol}$. 
In total, the jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras $\cL(\R^m \times \C^n) \to L_0[[z_j]]$.

@@

\begin{eg}
Suppose that $L$ is the trivial bundle on $\C^n$ and consider the abelian holomorphic-topological local Lie algebra 
\[
\Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(X) [-1]
\]
where the differential is just $\d_{dR} + \dbar$. 
Notice that with the shift functions on $\R^m \times \C^n$ are in cohomological degree $+1$.
Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
\[
\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
\]
Via the $n$-dimensional residue one can identify the algebra of local operators with 
\[
\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
\]

Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following single particle index
\[
\frac{1}{(1-q_1)\cdots (1-q_n)} .
\]
\end{eg}

@@

\subsection{Twisted global symmetry}

\brian{i think I will recall some of this in the language of `fields' in Section 1, but it'd be good to say a few words about operators.}

@@

After complexification, the six-dimensional superconformal algebra is $\lie{osp}(8|4)$. 
The holomorphic supercharge is a supertranslation 
\[
Q \in \Pi S_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which has the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator, and its cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

We consider the symmetry of the holomorphic twist of a six-dimensional superconormal theory with respect to the even subalgebra 
\[
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
\]

which acts in the following way: 
\begin{itemize}
\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect(\Hat{D}^3)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
where $(a_{ij}) \in \lie{sl}(3)$. 
\item The Lie algebra $\lie{sl}(2)$ is the subalgebra of $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$ consisting of constant formal series. 
\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by Euler vector field $\sum_i z_i \frac{\del}{\del z_i} \in \Vect(\Hat{D}^3).$
\end{itemize}

>>>>

\section{Twisted supergravity states}

@@

Generally speaking, twists of supersymmetric theories have a mixed holomorphic and topological behavior.

@@

%Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
%Let $\cV$ denote its sheaf of holomorphic sections.
%The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
%\[
%\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
%\]
%where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
%Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
%
%As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
%\begin{itemize}
%\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
%\[
%[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
%\]
%\end{itemize}
%A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
%
%\parsec
In part, the data of a holomorphic-topological theory in the BV formalism is prescribed by a holomorphic-topological local $L_\infty$ algebra $\cL$.
Without loss of generality we will assume our holomorphic-topological local $L_\infty$ algebra on $M \times X$ is of the form
\beqn\label{eqn:cL}
\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
\eeqn
where $L$ is a graded holomorphic vector bundle on $X$.
The differential is required to be of the form
\[
\d_{dR} + \dbar + Q^{hol}
\]
where $\d_{dR}$ is the de Rham differential acting on $M$, $\dbar$ is the Dolbeault operator acting on $X$, and $Q^{hol} \colon L \to L[1]$ is a holomorphic differential operator of cohomological degree $+1$. 
The higher $L_\infty$ structure maps of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators. 
For more details we refer to the definitions in \cite{GRWthf}.

In this situation, the factorization algebra of classical observables supported on an open set $U \subset M \times X$ is given by the Chevalley--Eilenberg cochains on the $L_\infty$ algebra $\cL(U)$. 
We will give a concise presentation for the {\em local} operators in a topological-holomorphic theory.

Suppose that $M \times X = \R^m \times \C^n$ and suppose that the bundle $L \to \C^n$ is translation invariant with fiber $L_0$ over $0 \in \R^m \times \C^n$.
We also assume that all structure maps of the $L_\infty$ algebra are translation invariant.
The jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras
\[
\cL(\C^n \times \R^m) \to L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] 
\]
The differential on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables. 
Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
\[
L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] \xto{\simeq} L_0 [[z_j]] 
\]
which sends $x_i, \d x_i,\zbar_j \d \zbar_j \mapsto 0$ is a quasi-isomorphism. 
The only remaining differential on the right hand side is~$Q^{hol}$. 
In summary, we see that the jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras $\cL(\R^m \times \C^n) \to L_0[[z_j]]$.

@@

Suppose that $L$ is the trivial bundle on $\C^n$ and consider the abelian holomorphic-topological local Lie algebra 
\[
\Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(\C^n) [-1]
\]
where the differential is just $\d_{dR} + \dbar$. 
Notice that with the shift, functions on $\R^m \times \C^n$ are in cohomological degree $+1$.
Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
\[
\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
\]
Via the $n$-dimensional residue one can identify the algebra of local operators with 
\[
\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
\]

Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following single particle index
\[
\frac{1}{(1-q_1)\cdots (1-q_n)} .
\]

@@

\subsection{Global symmetry for twisted fivebranes}

@@

After complexification, the~six-dimensional superconformal algebra is $\lie{osp}(8|4)$ whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
This algebra contains the $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
The holomorphic supercharge is a supertranslation 
\[
Q \in \Pi S_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which is characterized (up to equivalence) by the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

To compute characters of local operators the fivebrane worldvolume theory we will consider the symmetry of the holomorphic twist of a six-dimensional superconormal theory with respect to the even subalgebra 
\beqn\label{eqn:bosonic1}
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
\eeqn
We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.

In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification). 
Geometrically, this background is $AdS_7 \times S^4$. 
In \cite{RSW} we have proposed a twisted analog of the AdS background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twisted superconformal algebra.

We recall how the bosonic subalgebra \eqref{eqn:bosonic1} of this twisted superconformal algebra embeds as symmetries of the eleven-dimensional theory in this twisted background. 
This manifests as an embedding of this bosonic subalgebra into the ghosts of the eleven-dimensional theory.

For convenience we choose coordinates on the eleven manifold as
\[
\C^5 \times \R = \C_z^3 \times \C_w^2 \times \R_t
\]
with $z_i, i=1,2,3$ and $w_a, a=1,2$.
The stack of fivebranes wrap $w_1=w_2=t=0$. 
Important for us is to recall that part of the ghost system for our eleven-dimensional theory consists of divergence-free vector fields on $\C^5$ which are locally constant along $\R$.

\begin{itemize}
\item
The subalgebra $\lie{sl}(3)$ embeds as vector fields
\[
\sum_{ij} A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ij}) \in \lie{sl}(3) .
\]
\item
The subalgebra $\lie{gl}(1)$ is mapped to the element
\[
\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R)  .
\] 
Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $w=0$. 
\item 
The subalgebra $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
\[
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
\]
\end{itemize}

### 2022-06-06 fivebranes/twisted.tex
outline
all around

\subsection{A model for twisted supergravity}

@@

The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold. 
We opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.
The additional data of a theory in the BV formalism is a graded skew-symmetric pairing on this sheaf.

@@

@@

@@

\parsec[s:sugraobs]

In the BV formalism, the sheaf of fields of the eleven-dimensional theory is $\Pi \cL_{sugra}$. 
As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential. 
In other words, as a $\Z/2$ graded commutative dg algebra, the classical observables of the eleven-dimensional theory supported on an open set $U \subset X \times S$ is 
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]

@@

\parsec[s:singleobs]

The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
the cochain complex
\[
\clie^\bu\left(\cL_{single}(U)\right) .
\]

@@

\begin{prop}
There is a natural inclusion of of factorization algebras 
\[
\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
\]
which is dense at the level of cohomology. 
\end{prop}

We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.

\brian{old below}

@@

\begin{prop}
Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
\begin{itemize}
\item[(1)] there is a map of factorization algebras
\[
\clie^\bu(\cL_{\pi,sugra}) \to \pi_* \Obs_{sugra}
\]
which is dense in cohomology. 
\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
\beqn\label{eqn:decomp3}
\cL_{\pi,sugra} = \prod_{n \geq -1} \cV_{n} 
\eeqn
\item[(3)]
In weight zero, there is an equivalence of local Lie algebras on $Z$ 
\[
\cV_0 \simeq \cE(3|6)|Z .
\]
\end{itemize}
\end{prop}

>>>>

\subsection{A model for holomorphically twisted supergravity}

@@

The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.
In the first few sections we describe the fields and equations of motion of the eleven-dimensional theory.

@@

\parsec[s:sugrafields]

@@

We move on to give a complete description of our eleven-dimensional model.
In the BV formalism one introduces antifields and antighosts to the fields and ghosts that we have just described.
It is then fundamental to consider a graded skew-symmetric pairing between fields and antifields (ghosts and antighosts). 
Once such a pairing is introduced, one can opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.

@@

@@

@@

\begin{prop}
Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
\begin{itemize}
\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
\[
\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
\]
which is dense at the level of cohomology. 
\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
\beqn\label{eqn:decomp3}
\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
\eeqn
\item[(3)]
In weight zero, there is an equivalence of local Lie algebras on $Z$ 
\[
\cV_0 \simeq \cE(3|6)|Z .
\]
\end{itemize}
\end{prop}

%We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.

\parsec

\begin{prop}
On flat space 
\end{prop}

\appendix

@@
